Generalized Universe Hierarchies and First-Class Universe Levels

### 2021-02-23 paper.tex
correction

Lifted types correspond to types of object-level expressions; for
example, $\Bool_0 : \Ty_0\,\Gamma$ is the object-level type of Booleans, while
$\Lift\,\Bool_0$ is the meta-level type of $\Bool_0$-expressions, and $\Bool_1 :
\Ty_1\,\Gamma$ is the type of meta-level Booleans. It is possible to compute a
$\Lift\,\Bool_0$ from a $\Bool_1$. Given $b : \Tm_1\,\Gamma\,\Bool_1$, we can
construct
$\down(\mathsf{if}\,b\,\mathsf{then}\up\!\true_0\,\mathsf{else}\up\!\false_0) :
\Tm_0\,\Gamma\,\Bool_0$.

But there is no way to compute a $\Bool_1$ from a $\Lift\,\Bool_0$, since
$\Lift\,\Bool_0$ has no elimination rule in $\Ty_1$. Conceptually, terms
of $\Lift\,\Bool_0$ are \emph{expressions}, so they are not necessarily $\true$ or
$\false$, they can also be variables or neutral expressions, so the usual
Boolean elimination is not justified for them. In general, the setup ensures that
we can eliminate from positive types in $\Ty_1$ to their counterparts in
$\Ty_0$, but not the other way around, while negative types are preserved by
$\Lift$ up to type isomorphism.

>>>>

Lifted types correspond to types of object-level expressions; for example,
$\Bool_0 : \Ty_0\,\Gamma$ is the object-level type of Booleans, while
$\Lift\,\Bool_0$ is the meta-level type of $\Bool_0$-expressions, and $\Bool_1 :
\Ty_1\,\Gamma$ is the type of meta-level Booleans. It is possible to compute a
$\Bool_0$ from a $\Bool_1$. Given $b : \Tm_1\,\Gamma\,\Bool_1$, we can construct
$\down(\mathsf{if}\,b\,\mathsf{then}\up\!\true_0\,\mathsf{else}\up\!\false_0) :
\Tm_0\,\Gamma\,\Bool_0$.

But there is no way to compute a $\Bool_1$ from a $\Bool_0$: we can try to lift
the input, but there is no elimination rule for $\Lift\,\Bool_0$ in
$\Ty_1$. Conceptually, terms of $\Lift\,\Bool_0$ are \emph{expressions}, so they
are not necessarily $\true$ or $\false$, they can also be variables or neutral
expressions, so the usual Boolean elimination is not justified for them. In
general, the setup ensures that we can eliminate from positive types in $\Ty_1$
to their counterparts in $\Ty_0$, but not the other way around, while negative
types are preserved by $\Lift$ up to type isomorphism.
